### 2018-06-15 Paper/ack.tex
..

M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
National Science Foundation (Grant No. 1404823, CDSE Program). M. Vohra
would also like to sincerely thank Dr. Xun Huan at Sandia National Labs for
his guidance pertaining to the usage of TChem for the chemical kinetics application
in this work.

>>>>

M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
National Science Foundation (Grant No. 1404823, CDSE Program). 
C. Safta was supported by the U.S. Department of Energy, Office of Science,
Basic Energy Sciences, as part of the Computational Chemical Sciences Program.
M. Vohra would also like to sincerely thank Dr. Xun Huan at Sandia National Labs for
his guidance pertaining to the usage of TChem for the chemical kinetics application
in this work. Sandia National Laboratories is a multimission laboratory managed 
and operated by National Technology \& Engineering Solutions of Sandia, LLC, 
a wholly owned subsidiary of Honeywell International Inc., for the 
U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525. 
The views expressed in the article do not necessarily represent the
views of the U.S. Department Of Energy or the United States Government.

### 2018-06-15 Paper/app.tex
..

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The mechanism comprises of 19 reactions including chain reactions,
dissociation/recombination reactions, and formation and consumption
of intermediate species: HO$_2$ and H$_2$O$_2$, as provided below
in Table~\ref{tab:kinetics}.

@@

The reaction rate for the $i^{th}$ reaction as a function of temperature
is given as follows:
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
universal gas constant. We focus on quantifying the uncertainty in the
\emph{ignition delay} due to uncertainty associated with the pre-exponent,
$A_i$ for each reaction. Hence, the total number of uncertain parameters in the
present case is 19.  The $A_i$'s are considered to be uniformly distributed in
the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
estimate corresponding to the $i^{th}$ reaction. TChem~\cite{Safta:2011}, an
open source C package was used for simulating temperature and concentration
evolution during the progress of reactions $\mathcal{R}_1$--$\mathcal{R}_{19}$,
and determining the ignition delay. The set of nominal values used in the
computations, for parameters in~\eqref{eq:rate} are provided
in~\cite{Yetter:1991}.

>>>>

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
source of clean energy for applications such as 
transportation~\cite{Das:1996}. 
The mechanism comprises of 19 reactions including chain reactions,
dissociation/recombination reactions, and formation and consumption
of intermediate species as provided below in Table~\ref{tab:kinetics}.

@@

The reaction rate for the $i^{th}$ reaction as a function of temperature
is given as follows:
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
universal gas constant. 
The TChem~\cite{Safta:2011} software package is used to model homogenous
ignition at constant pressure for a range of initial conditions for the
fuel-oxidizer mixture. During the simulation, the fuel-oxidizer mixture goes 
through a radical build-up phase followed by a sharp increase in temperature
as heat is realeased during the thermal runaway. We focus on quantifying the 
uncertainty in the \emph{ignition delay} due to uncertainty associated 
with the pre-exponent, $A_i$, for each reaction. The ignition delay 
is defined as the inflection point on the temperature profile during the thermal
runaway. The total number of uncertain parameters in the
present case is 19.  The $A_i$'s are considered to be uniformly distributed in
the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
estimate corresponding to the $i^{th}$ reaction.
The set of nominal values used in the computations, for parameters 
in~\eqref{eq:rate} are provided
in~\cite{Yetter:1991}.
